Cartogram Mapping and its Application to Cancer Data Visualization

### 2019-09-27 review_article.Rmd
table

|  | Choropleth | Contiguous | Non-contiguous | Dorling | Tile maps | Geofacets |
|:-----------:|------------|-----------|---------------|---------|-----------|----------|
| Spatial distortion | N | Y | Y | Y | Y | Y |
| Preserves neighbors | Y | Y | Y | S | S | S |
| Conceals small areas | Y | S | N | N | N | N |
| Uniform shape | N | N | N | Y | Y | Y |
| Univariate only | Y | Y | Y | S | S | N |
| Manual construction | N | N | N | N | Y | Y |

>>>>

|                     | Choropleth | Contiguous | Non-contiguous | Dorling | Tile maps | Geofacets |
|:-----------:|------------|-----------|---------------|---------|-----------|----------|
|Spatial distortion   |  N  |  Y  |  Y  |  Y  |  Y  |  Y  |
|Preserves neighbors  |  Y  |  Y  |  Y  |  S  |  S  |  S  |
|Conceals small areas |  Y  |  S  |  N  |  N  |  N  |  N  |
|Uniform shape        |  N  |  N  |  N  |  Y  |  Y  |  Y  |
|Univariate only      |  Y  |  Y  |  Y  |  S  |  S  |  N  |
|Manual construction  |  N  |  N  |  N  |  N  |  Y  |  Y  |
